%-------------------------
% Enhanced ATS-Optimized Resume in LaTeX
% Author : Nikhil Mishra
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting (using all uppercase for standard headers)
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\Large
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{%
  \item\small{#1\vspace{-2pt}}%
}

\newcommand{\resumeSubheading}[4]{%
  \vspace{-2pt}\item%
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}%
    \textbf{#1} & #2 \\%
    \textit{\small #3} & \textit{\small #4} \\%
  \end{tabular*}\vspace{-7pt}%
}

\newcommand{\resumeProjectHeading}[2]{%
  \item%
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}%
    \small \textbf{#1} & #2 \\%
  \end{tabular*}\vspace{-7pt}%
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge Nikhil Mishra} \\ \vspace{1pt}
  \small 9975646076 $|$ \href{mailto:nm30472@gmail.com}{nm30472@gmail.com} $|$
  \href{https://iam.nikhilmishra.live}{iam.nikhilmishra.live} $|$
  \href{https://links.nikhilmishra.live}{links.nikhilmishra.live} $|$
  \href{https://github.com/kaalpanikh}{github.com/kaalpanikh} $|$
  \href{https://linkedin.com/in/nikhil-mishra}{linkedin.com/in/nikhil-mishra} $|$
  \href{https://x.com/kaalpanikhitis}{x.com/kaalpanikhitis}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{PROFESSIONAL SUMMARY}
  \resumeSubHeadingListStart
    \item{
      DevOps Engineer with proven expertise in architecting, automating, and deploying scalable cloud infrastructures. Transitioned legacy systems to Kubernetes/EC2 microservices, cutting AWS costs from \$130 to \$10/month. Expert in designing CI/CD pipelines, container orchestration, and Infrastructure as Code using Docker, Terraform, and Ansible. Publishes DevOps insights via a blog (1000+ views) and maintains a robust GitHub portfolio.
    }
  \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{WORK EXPERIENCE}
  \resumeSubHeadingListStart
    \resumeSubheading
      {DevOps Engineer}{Jul. 2024 -- Present}
      {Hooked}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Migrated from a monolithic web app to a Kubernetes/EC2 microservices architecture, boosting scalability and reducing latency by 35\%.}
        \resumeItem{Built and optimized CI/CD pipelines for 20+ repositories using Dockerhub and GitHub Actions, cutting deployment time by 30\%.}
        \resumeItem{Developed a Discord bot for real-time serverless cost monitoring, enabling proactive budget control.}
        \resumeItem{Optimized AWS usage to achieve a 90\% reduction in monthly expenses.}
        \resumeItem{Engineered a serverless monitoring solution on Runpod for 20+ services and deployed ML models that improved system reliability by ~15\%.}
        \resumeItem{Implemented Infrastructure as Code with Terraform and Ansible for consistent, scalable deployments.}
      \resumeItemListEnd
    
    \resumeSubheading
      {SRE Intern}{May 2023 -- Aug. 2023}
      {Dukaan}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Managed cloud infrastructure and migrated to bare metal, reducing latency by 20\%.}
        \resumeItem{Integrated Grafana with the ELK stack for precise log analysis and performance monitoring.}
        \resumeItem{Automated routine tasks using Bash/Python, increasing efficiency by 40\%.}
        \resumeItem{Collaborated with teams to reduce mean time to recovery (MTTR) by 25\%.}
        \resumeItem{\textbf{Link:} \href{https://dukaan.nikhilmishra.live}{dukaan.nikhilmishra.live}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Roadmap.sh DevOps Projects}}{}
      \resumeItemListStart
        \resumeItem{Executed 20+ projects on automation, containerization, CI/CD, and cloud deployments (GitHub: \href{https://github.com/kaalpanikh}{github.com/kaalpanikh}).}
        \resumeItem{Highlighted projects include legacy-to-Kubernetes migrations and automated monitoring solutions that significantly reduced costs.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{iam.nikhilmishra.live Portfolio}}{\href{https://iam.nikhilmishra.live}{iam.nikhilmishra.live}}
      \resumeItemListStart
        \resumeItem{Central hub for all DevOps projects, technical articles, and blog posts.}
        \resumeItem{Site analytics: 107 unique visitors and 8.92k total requests in the past 30 days.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Technical Blog Contributions}}{\href{https://nikhilmishra.live}{nikhilmishra.live}}
      \resumeItemListStart
        \resumeItem{Authored in-depth DevOps articles with 1000+ page views on cloud automation and multi-tier deployments.}
        \resumeItem{Featured posts: \textbf{I Escalated My App to the Cloud!}, \textbf{I Can Set Up a Multi-Tier App Locally for You}, \textbf{Custom Subdomain Forwarding with Cloudflare}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{SKILLS}
  \resumeSubHeadingListStart
    \item{
      \textbf{Cloud \& Virtualization:} AWS, EC2, Serverless, Kubernetes, VPC, Cloud Networking \\
      \textbf{Containerization:} Docker, Kubernetes, Microservices, Container Registries \\
      \textbf{IaC \& Automation:} Terraform, Ansible, Jenkins, GitHub Actions, GitOps \\
      \textbf{Monitoring:} ELK, Prometheus, Grafana, Netdata \\
      \textbf{Scripting:} Bash, Python, Shell Scripting \\
      \textbf{Security \& Networking:} fail2ban, DNS Management, Firewall Management, Cloudflare Workers \\
      \textbf{Methodologies:} Agile, Cost Optimization, Performance Tuning, Incident Management
    }
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Mumbai University}{Boisar, Maharashtra, India}
      {Bachelor of Engineering in Computer Engineering}{Aug. 2021 -- May 2025 (Expected)}
  \resumeSubHeadingListEnd

%-----------AWARDS & CERTIFICATIONS-----------
\section{AWARDS \& CERTIFICATIONS}
  \resumeSubHeadingListStart
    \resumeItem{Won 1st prize (₹5000 cash) at the Shark Tank Competition at Sardar Patel Institute of Technology, Andheri, for the app idea \textbf{Jai Kisan}.}
    \resumeItem{Participated in Buildspace's Nights and Weekends Season 4, refining practical DevOps and automation skills.}
  \resumeSubHeadingListEnd

\end{document}
